A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-18 doc/large_strain.tex
a bit more CM

% put your own definitions here:
% \renewcommand\thesubfigure{(\alph{subfigure})}
\def\gz  #1{           \mbox{$\boldsymbol{#1}$}}
% \DeclareMathAlphabet{\bsf}{OT1}{cmss}{bx}{n}
% \def\msf  #1{           \mbox{\!\!      $\sf #1$}}
% \def\Grad #1 {{\rm Grad} #1}
% \def\grad #1 {{\rm grad} #1}
\def\Div {\mbox{Div\,}}
\def\div {\mbox{div\,}}
\def\d {\,\mbox{d}}
\def\D {\,\mbox{D}}
% \newcommand{\norm}[1]{\left\lvert #1 \right\rvert}
%\newcommand\normDouble[1]{\left\lVert#1\right\rVert}
%\newcommand{\normXY}[1]{\lvert #1 \rvert_{2d}}
%\newcommand{\dbracket}[1]{\left[\!\!\left[ #1 \right]\!\!\right]}

@@

Deformation of the body $\mcl B$ from the reference configuration $\mcl B_0$ to the current configuration $\mcl B_t$
is defined via the mapping $\gz x = \gz \varphi (\gz X,t)$.
%
Linear deformation map is assumed
$\d \gz x = \gz F \cdot \d \gz X$,
where $\gz F := \gz \nabla_{X} \, \gz \varphi$ is the deformation gradient.
For conservative systems without the volumetric load the total potential energy functional $\mcl E$ is introduced as
\begin{align}
\mcl E =
\int_{\mcl B_0} \mcl \psi(\gz \varphi, \gz F; \gz X) \,
- \int_{\partial \mcl B_0^N} \gz T \cdot \gz u \d S \, ,
\end{align}
where $\gz T$ is the prescribed loading at the Neumann part of the boundary $\partial \mcl B_0^N$ in reference configuration, and $\mcl \psi$ denotes the strain-energy per unit reference volume.

@@

>>>>

% put your own definitions here:
% \renewcommand\thesubfigure{(\alph{subfigure})}
\def\gz  #1{           \mbox{$\boldsymbol{#1}$}}
% \DeclareMathAlphabet{\bsf}{OT1}{cmss}{bx}{n}
% \def\msf  #1{           \mbox{\!\!      $\sf #1$}}
\def\Grad #1 {{\rm Grad} #1}
\def\grad #1 {{\rm grad} #1}
\def\Div {\mbox{Div\,}}
\def\div {\mbox{div\,}}
\def\d {\,\mbox{d}}
\def\D {\,\mbox{D}}
% \newcommand{\norm}[1]{\left\lvert #1 \right\rvert}
%\newcommand\normDouble[1]{\left\lVert#1\right\rVert}
%\newcommand{\normXY}[1]{\lvert #1 \rvert_{2d}}
%\newcommand{\dbracket}[1]{\left[\!\!\left[ #1 \right]\!\!\right]}

@@

Deformation of the body $\mcl B$ from the reference configuration $\mcl B_0$ to the current configuration $\mcl B_t$
is defined via the mapping $\gz x = \gz \varphi (\gz X,t)$.
%
Linear deformation map is assumed
$\d \gz x = \gz F \cdot \d \gz X$,
where $\gz F := \Grad \, \gz \varphi$ is the deformation gradient.
For conservative systems without the volumetric load the total potential energy functional $\mcl E$ is introduced as
\begin{align}
\mcl E =
\int_{\mcl B_0} \mcl \psi(\gz \varphi, \gz F; \gz X) \d V \,
- \int_{\partial \mcl B_0^N} \gz T \cdot \gz u \d S \, ,
\end{align}
where $\gz T$ is the prescribed loading at the Neumann part of the boundary $\partial \mcl B_0^N$ in reference configuration, and $\mcl \psi$ denotes the strain-energy per unit reference volume.

@@

The stationary conditions yield
\begin{align}
F(\gz u, \delta \gz u) =
\int_{\mcl B_0} \gz P : \Grad \, \delta \gz u \d V \,
-
\int_{\partial \mcl B_0^N} \gz T \cdot \delta \gz u \d S
= 0 \, ,
\end{align}
where $\gz P := \partial \mcl \psi / \partial \gz F$ is the Piola stress.
